Papers I Love

### 2017-05-07 texts/dev/PapersILove.tex
.

\subsection{Data Fusion}
\begin{enumerate}
	\item {A Generic Architecture for Fusion-Based Intrusion Detection Systems\\
\url{https://rcdeboer.home.xs4all.nl/rcdb_thesis.pdf}}
\end{enumerate}

\section{Mathematics}
\subsection{Real Analysis}
\begin{enumerate}
	\item {COISAS QUE O LUÍS PRECISA APRENDER\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}

>>>>

\subsection{Data Fusion}

\begin{enumerate}
	\item {A Generic Architecture for Fusion-Based Intrusion Detection Systems\\
\url{https://rcdeboer.home.xs4all.nl/rcdb_thesis.pdf}}
\end{enumerate}

\subsection{Artificial Intelligence}
\begin{enumerate}
	\item {Computing Machinery and Intelligence\\ \url{http://orium.pw/paper/turingai.pdf}}
\end{enumerate}

\subsection{Text Mining}
\begin{enumerate}
	\item {Text Mining Infrastructure in R\\ \url{https://www.jstatsoft.org/article/view/v025i05}}
\end{enumerate}

\subsection{VIPs}
\begin{enumerate}
	\item {Richard Bellman's contributions to computer science\\\url{http://www.sciencedirect.com/science/article/pii/0022247X86901460}}
\end{enumerate}

\section{Mathematics}
\subsection{Real Analysis}
\begin{enumerate}
	\item {Coisas que o Luís precisa aprender\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}

\section{Science}
\subsection{Research}
\begin{enumerate}
	\item {Why Most Published Research Findings Are False\\
	\url{http://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.0020124}}
\end{enumerate}
